---
title: "Where to Find the Best Job?"
output:
  html_document: default
  html_notebook: default
  pdf_document: default
---
This project tries to answer which state and induatry is the best place to work in America, by analyzing working hours and wage data by states and industries. It mainly can be divided into 3 part.

####General Analysis                
*What's the working environment in America?* Data analysis and visualization of the average working hours and wage by different states.
       
####Occupations and Industries Analysis     
*Which job or industry is the best to work for?* To find the best occupation and industry to work onIllustration of Top 5 occupations and industries which have the best working hours and wage ratio.
          
####Computer and Mathmatical Occupations Analysis
*If I stay with what I learnt, where should I go?* Focusing on the computer and Mathmatical Occupations, research on the working hours and wage by different states.

       
##Set up the Bench
```{r lib,message=FALSE}
library(readr)
library(dplyr)
library(maps)
library(leaflet)
library(rbokeh)
library(fmsb)
```

##Read Data
```{r toload,message=FALSE}
setwd("C:/Users/Administrator/Desktop/ADS/Proj 1/Data")
load(".RData")

#a14=read_csv("ss14pusa.csv")
#b14=read_csv("ss14pusb.csv")
#all14=rbind(a14,b14)
#rm(a14);rm(b14)
#gc();Sys.sleep(10);gc() #To make sure clean all memory in case of crash

ST_name=read.csv("statenames.csv") #The redundant space in abbr column has been removed in Excel
occupa=read.csv("OCCP.csv")
```


##Clean Dataset
```{r}
#selct=select(all14,OCCP,ST,WAGP,AGEP,JWMNP,ESR,SCHL,SEX,WKHP,NAICSP,PWGTP,POWSP,POWPUMA)%>%
#      na.omit()%>%
#      mutate(WAGP=as.numeric(WAGP),
#             AGEP=as.numeric(AGEP),
#             WKHP=as.numeric(WKHP),
#             JWMNP=as.numeric(JWMNP),
#             PWGTP=as.numeric(PWGTP),
#             ST=as.integer(ST),
#             SCHL=as.integer(SCHL),
#             SEX=as.integer(SEX),
#             OCCP=as.integer(OCCP))%>%
#       merge(occupa,by="OCCP")
      

group_ST=group_by(selct,ST)
sumrz_ST=summarise(group_ST,
                   Meanwage=weighted.mean(WAGP,w=PWGTP),
                   MeanAGEP=weighted.mean(AGEP,w=PWGTP),
                   MeanWKHP=weighted.mean(WKHP,w=PWGTP),
                   MeanJWMNP=weighted.mean(JWMNP,w=PWGTP)
                    )%>%
          mutate(ST.map=match((ST_name$abbr[-52]),state.fips$abb,nomatch=99))%>%
          mutate(abb=state.fips$abb[ST.map])%>%
          arrange(ST.map)
map.data=merge(state.fips,sumrz_ST,by="abb",all=T)%>%
         arrange(ST.map)
```

##Data Analysis and Visualization
###1.General Analysis: What's the working environment in America?
####Average Annual Wage by States





[Figure 1.Map for Average Wage](map1.html)

This graph shows the distribution of the average wage of different states. As it shows, _The Northeast region_ generally has a higher salaries than the rest part of the contries. _The west coast_ also shows higher wage tendency. _Colorado, Minnesota and Illinois_ also stand out from the middle. Colorado has a reputation on its aerospace and aviation industry. Apart from agriculture, Minnesota has a strong root of bioscience, is one of the biggest cribs of medical profesionals. Chicago as the third biggest city in USA definitely contributes on the deeper color of Illinois in this graph.


####Average Working Hours per week by States

[Figure 2.Map for Average Working Hour](map2.html)

This Graph shows the average working hours by different state. The states which shows longer averagely working hours are most likely depends on agriculture industry. Surprisingly, New York people is not the most hard working people among the country.


####Work Life balance Ratio by States

[Figure 3.Map for Hour Salary](map3.html)


Laziness is human nature. Don't you want a job which pays tons of money and only requireds you show up at work for an hour on Friday before you head out? We calculated work life balance ratio by working hours and wage. Apparently, people who works "in the office" and have higher education generally have a sweeter life. But the problem is the data shows smaller diversities of working hours among the states, so this graph's data is mainly dominant by the wage differences.


###2.Occupations and Industries Analysis: Which job or industry is the best to work for? 
####Regroup Data by Occupations and Industries
```{r}
group_OCCPABB=group_by(selct,OCCABB)
sumrz_OCCPABB=summarise(group_OCCPABB,
                   Meanwage=weighted.mean(WAGP,w=PWGTP),
                   MeanAGEP=weighted.mean(AGEP,w=PWGTP),
                   MeanWKHP=weighted.mean(WKHP,w=PWGTP),
                   MeanJWMNP=weighted.mean(JWMNP,w=PWGTP),
                   MeanSCHL=weighted.mean(SCHL,w=PWGTP),
                   MeanSEX=weighted.mean(SEX,w=PWGTP),
                   Count=sum(PWGTP)
)

group_OCCP=group_by(selct,OCCP)
sumrz_OCCP=summarise(group_OCCP,
                        Meanwage=weighted.mean(WAGP,w=PWGTP),
                        MeanAGEP=weighted.mean(AGEP,w=PWGTP),
                        MeanWKHP=weighted.mean(WKHP,w=PWGTP),
                        MeanJWMNP=weighted.mean(JWMNP,w=PWGTP),
                        MeanSCHL=weighted.mean(SCHL,w=PWGTP),
                        MeanSEX=weighted.mean(SEX,w=PWGTP),
                        Count=sum(PWGTP),
                        JOBNAME=OCCUPATION[1]
)

```


####Occupations and Industries Working Conditions Comparison
```{r}
n <- nrow(sumrz_OCCP)
ramp <- colorNumeric(
  palette = "Blues",
  domain = sumrz_OCCP$MeanSCHL
)
options(viewer = NULL)
```
```{r}
figure() %>%
  ly_points(x=Meanwage,y=MeanWKHP, hover=JOBNAME,color = ramp(sumrz_OCCP$MeanSCHL), size = 20*Count/max(Count),data=sumrz_OCCP) %>%
  tool_box_select() %>%
  tool_lasso_select()%>%
  x_axis("Average Wage",number_formatter = "numeral", format = "0,000")%>%
  y_axis("Average Working Hour",number_formatter = "numeral", format = "0,000")
```
Physicians and surgens won the best paid occupation without a doubt, and their wage is way higher than other occupations. All other managing and legal related occupations appear a lead speaking of wage.

Figure 4. Occupation Attribution (By Occupation)

Among all the occupations, legal occupations won the best paid occupation. Business and Managing occupations have the best work life balance. Finance, engineering and computer mathmatical occupations are pretty close to managing roles speaking of working hours and wages. In general, the graph illustrates the old saying, no pain no gain.
```{r}

figure() %>%
  ly_points(x=Meanwage,y=MeanWKHP, hover=OCCABB,color = ramp(sumrz_OCCPABB$MeanSCHL), size = Count/min(Count),data=sumrz_OCCPABB) %>%
  tool_box_select() %>%
  tool_lasso_select()%>%
  x_axis("Average Wage",number_formatter = "numeral", format = "0,000")%>%
  y_axis("Average Working Hour",number_formatter = "numeral", format = "0,000")
  

```
Figure 5. Occupation Attribution (By Category)

###3.Where can WE(statistician) choose?


[Figure 6. Map for Average Wage (Occupation Category: CMM-Computer and Mathematical Occupations)](map4.html)
According to the map, Northeast including New York City, California and Washiton's computer and mathematical occupaitions are the best place for data scientists, programmer or statistians to work where provides the best work life balance. Since most of tech companies who requires more computer and mathmatical profesionals are located in northeat cities and the west coasts.

[Figure 7. Map for Average Working Hour (Occupation Category: CMM-Computer and Mathematical Occupations)](map5.html)

[Figure 8.Map for Hour Salary (Occupation Category: CMM-Computer and Mathematical Occupations)](map6.html)

According to the map, Northeast including New York City, California and Washiton's computer and mathematical occupaitions are the best place for data scientists, programmer or statistians to work where provides the best work life balance. Since most of tech companies who requires more computer and mathmatical profesionals are located in northeat cities and the west coasts.
